---
title: "Project_Jeenil"
output: html_document
---

#Reading the data
```{r}
MA.vs.US <- read.csv("CSV's/Overall Homelessness in 2018.csv")
```

#Basic Data Exploration

Summary on the Normalized Data Column 
```{r}
summary(MA.vs.US$X..Homelessness)
```
#Graph 
```{r}
library(ggplot2)

ggplot(data=MA.vs.US, aes(x = State, y= X..Homelessness)) +
  geom_bar(stat="identity")

```

#Variables 
```{r}
Sample_mean = mean(MA.vs.US$X..Homelessness)
n_val = nrow(MA.vs.US)
sd = sd(MA.vs.US$X..Homelessness)
```

#95% Confience Interval
```{r}
error = 1.96 * (sd / sqrt(n_val))
left = Sample_mean - error
right = Sample_mean + error
  
ci = c(left,right)
ci 
```
With the 95% Confidence we say that the Overall homelessness in the US falls between (0.001182537 and 0.002018864). The data is normalized. 

#Hypotheses Testing
#Step 1

We believe that MA’s Overall Homelessness is in order with the overall Homeless in the United States. To check if we can accept this hypothesis we need to run a two-tailed Hypothesis test to see if there is a diffence in the Homeless in MA vs. the rest of the country. 
1. Define Hypotheses 

Null = All non-MA states have the same overall homelessness as MA
 
  H0: Mu = 0.0029075
  
Alternate Hypothesis = All non-MA states have a different overall homelessness as MA 

  Ha: Mu != 0.0029075
  
#Step 2  
2. Alpha Level we will use is 0.05.
  Alpha = 0.05

#Step 3
3. Calculating the T stastic
```{r}
mu0 = mean(MA.vs.US$X..Homelessness[-1])
x_bar <- 0.0029075  
n = nrow(MA.vs.US)
sigma = sd(MA.vs.US$X..Homelessness[-1])

t = (x_bar - mu0)/(sigma / sqrt(n))
t
```
#Step 4
Calculate the P Value (Two-tail Test)
```{r}
pval = 2 * pt(-abs(t), df = n - 1 )
pval
```
Conclusion:
We reject the null hypothesis that the total homelesness in MA is the same as the rest of the country.There is statistically significant evidence to suggest that the total homelessness in MA is different than the rest of the country, and that the observed difference between the means is unlikely to be due to random chance. 



