---
title: "project_corey"
author: "Corey Kozlovski"
date: "11/19/2019"
output: html_document
---

#One-Sided Hypothesis Testing (non-MA vs MA)

#Reading the data
```{r}
MA.vs.US <- read.csv("CSV's/Overall Homelessness in 2018.csv")
```


#Random Summary Statistics
```{r}
hist(MA.vs.US$X..Homelessness)
plot(MA.vs.US$ï..State, MA.vs.US$Overall.Homeless..2018)

```
#Step 1
Null: All non-MA states have a greater than or equal to overall homelessness as MA
H0: Mu >= 0.0029075

Alternate Hypothesis: All non-MA states have a lower overall homelessness than MA
Ha: Mu < 0.0029075

#Calculating Manually
#Step 2
The Alpha level we will use is .05.

#Step 3
Calculating the T-Statistic
```{r}
x_bar <- 0.0029075
n <- nrow(MA.vs.US) - 1
sd <- sd(MA.vs.US$X..Homelessness[-1])
mu_0 <- mean(MA.vs.US$X..Homelessness[-1])
t_stat <- (x_bar - mu_0)/(sd/sqrt(n))
t_stat
```
#Step 4
Calculating the P-Value
```{r}
p_val <- pt(-abs(t_stat), df = n-1)
p_val
```

#Calculating with t.test
```{r}
t.test(MA.vs.US$X..Homelessness[-1], mu=0.0029075, alternative = 'less')
```
#Step 5
Conclusion

From both the manual calculations and from using the t.test function in R, we find that the p value is 6.388e-08. Since this value is lower than our alpha, .05, we can reject the null hypothesis, meaning that all non-MA states do not have a greater than or equal to overall homelessness as MA. We have statisically significant evidence to conclude that non-MA states have a lower overall homelessness than MA does. This tells us that MA has a higher homelessness value than the rest of the nation on average.



#One-Sided Hypothesis Testing (Non-Boston Coc's vs Boston Coc)

#Read in the data
```{r}
MA.CoCs = read.csv("CSV's/MA CoC's.csv")
```

#Step 1
Null: All non-Boston CoC's in MA have a greater than or equal to overall homelessness as Boston
H0: Mu >= 0.008908942

Alternate Hypothesis: All non-Boston CoC's in MA have a lower overall homelessness than Boston
Ha: Mu < 0.008908942

#Calculating Manually
#Step 2
The Alpha level we will use is .05.

#Step 3
Calculating the T-Statistic
```{r}
x_bar <- 0.008908942
n <- nrow(MA.CoCs) - 1
sd <- sd(MA.CoCs$Ratio.of.Homeless[-1])
mu_0 <- mean(MA.CoCs$Ratio.of.Homeless[-1])
t_stat <- (x_bar - mu_0)/(sd/sqrt(n))
t_stat
```
#Step 4
Calculating the P-Value
```{r}
p_val <- pt(-abs(t_stat), df = n-1)
p_val
```

#Calculating with t.test
```{r}
t.test(MA.CoCs$Ratio.of.Homeless[-1], mu=0.008908942, alternative = 'less')
```
#Step 5
Conclusion
Since our p value is significantly less than our alpha, .05, we can reject our null hypothesis that all non-Boston CoC's have a greater than or equal to homelessness value than Boston's CoC. We have statisically significant evidence that the non-Boston CoC's have a lower average homelessness than Boston's CoC, which tells us that Boston has the highest homelessness value in comparison to the rest of MA.



